3D Magnetic modelling of ellipsoidal bodies

### 2017-02-21 manuscript/manuscript.tex
preliminary version of the subsection defining chi max

\subsubsection{Relationship between $\chi$ and the magnetization error}

In the case of isotropic susceptibility, the resultant magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic}) may be determined by solving the
following linear system:
\begin{equation}
\mathbf{\Lambda}^{-1} \, \mathbf{M} = \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-K-isotropic-inverse-Lambda}
\end{equation}
where, according to Eq. \ref{eq:Lambda-K-isotropic},
\begin{equation}
\mathbf{\Lambda}^{-1} = \mathbf{V}
\left( \mathbf{I} - \chi \, \tilde{\mathbf{N}}^{\dagger} \right)
\mathbf{V}^{\top} \: .
\label{eq:inverse-Lambda}
\end{equation}
As we have already pointed out, the approximated
magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
represents the particular case in which the matrix 
$\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda-K-isotropic}),
and consequently the matrix $\mathbf{\Lambda}^{-1}$
(Eq. \ref{eq:inverse-Lambda}), are close to the identity.
Our goal in this subsection is to bound the norm of the
difference between the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
and the approximated magnetization $\breve{\mathbf{M}}$
(Eq. \ref{eq:M-approx}).

@@

By using the concept of vector norm and its corresponding
operator norm \citep{demmel1997, golub2013}, we may use Eq.
\ref{eq:perturbed-M-system} to write the following inequality:
\begin{equation}
\frac{\| \delta \mathbf{M} \|}{\| \mathbf{M} \|} \leq
\| \delta \mathbf{\Lambda}^{-1} \| \: .
\label{eq:perturbed-M-inequality}
\end{equation}
where $\| \delta \mathbf{M} \|$ and $\| \mathbf{M} \|$
denote Euclidean norms (or 2-norms) and the term 
$\| \delta \mathbf{\Lambda}^{-1} \|$ denotes the matrix 2-norm
of $\delta \mathbf{\Lambda}^{-1}$, which is given by
\begin{equation}
\| \delta \mathbf{\Lambda}^{-1} \| = \chi \,
\tilde{n}^{\dagger}_{33} \: ,
\label{eq:norm-perturbed-inverse-Lambda}
\end{equation}
where $\tilde{n}^{\dagger}_{33}$ is defined in the 
following sections, depending on the ellipsoid
type.

@@

\subsection{Susceptibility}

>>>>

\subsubsection{Relationship between $\chi$ and the relative error in $\breve{\mathbf{M}}$}

In the case of isotropic susceptibility, the resultant magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic}) may be determined by solving the
following linear system:
\begin{equation}
\mathbf{\Lambda}^{-1} \, \mathbf{M} = \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-K-isotropic-inverse-Lambda}
\end{equation}
where, according to Eq. \ref{eq:Lambda-K-isotropic},
\begin{equation}
\mathbf{\Lambda}^{-1} = \mathbf{V}
\left( \mathbf{I} - \chi \, \tilde{\mathbf{N}}^{\dagger} \right)
\mathbf{V}^{\top} \: .
\label{eq:inverse-Lambda}
\end{equation}
As we have already pointed out, the approximated
magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
represents the particular case in which the matrix 
$\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda-K-isotropic}),
and consequently the matrix $\mathbf{\Lambda}^{-1}$
(Eq. \ref{eq:inverse-Lambda}), are close to the identity.
%Our goal in this subsection is to bound the norm of the
%difference between the true magnetization $\mathbf{M}$
%(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
%and the approximated magnetization $\breve{\mathbf{M}}$
%(Eq. \ref{eq:M-approx}).

@@

By using the concept of vector norm and its corresponding
operator norm \citep{demmel1997, golub2013}, we may use Eq.
\ref{eq:perturbed-M-system} to write the following inequality:
\begin{equation}
\frac{\| \delta \mathbf{M} \|}{\| \mathbf{M} \|} \leq
\| \delta \mathbf{\Lambda}^{-1} \| \: .
\label{eq:perturbed-M-inequality}
\end{equation}
where $\| \delta \mathbf{M} \|$ and $\| \mathbf{M} \|$
denote Euclidean norms (or 2-norms) and the term 
$\| \delta \mathbf{\Lambda}^{-1} \|$ denotes the matrix 2-norm
of $\delta \mathbf{\Lambda}^{-1}$.
By using Eqs. \ref{eq:inverse-Lambda} and \ref{eq:perturbed-inverse-Lambda}
and the orthogonal invariance of the matrix 2-norm
\citep{demmel1997, golub2013}, we define
$\| \delta \mathbf{\Lambda}^{-1} \|$ as follows:
\begin{equation}
\| \delta \mathbf{\Lambda}^{-1} \| = \chi \,
\tilde{n}^{\dagger}_{33} \: ,
\label{eq:norm-perturbed-inverse-Lambda}
\end{equation}
where $\tilde{n}^{\dagger}_{33}$ is defined in the 
following sections, depending on the ellipsoid
type.
It is worth, however, to stress that $\tilde{n}^{\dagger}_{33}$ is
a scalar function of the ellipsoid semi-axes.
In Eq. \ref{eq:perturbed-M-inequality}, the ratio
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$ represents the
\textit{relative error} in the approximated magnetization
$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) with respect
to the true magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-K-isotropic}
and \ref{eq:M-K-isotropic-inverse-Lambda}).

Given a target relative error
$\epsilon = \| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$
and an ellipsoid
with given semi-axes, we may use the inequality
represented by Eq. \ref{eq:norm-perturbed-inverse-Lambda}
to define
\begin{equation}
\chi_{max} = \frac{\epsilon}{\tilde{n}^{\dagger}_{33}} \: ,
\label{eq:max-chi}
\end{equation}
which represents the maximum isotropic susceptibility 
that the ellipsoidal body can assume in order o guarantee
a relative error lower than or equal to $\epsilon$.
For isotropic susceptibilities greater than $\chi_{max}$,
there is no guarantee that the relative error in the
approximated magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
with respect to the true magnetization $\mathbf{M}$ 
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
is lower than or equal to $\epsilon$. The geoscientific community
has been using $\chi_{max} = 0.1$ SI as a limit value for
neglecting the self-demagnetization and, consequently,
use magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
as a good approximation of the true magnetization $\mathbf{M}$ 
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
Equation \ref{eq:max-chi}, on the other hand, defines $\chi_{max}$ 
as a function of the ellipsoid semi-axes, according to a
user-specified relative error $\epsilon$.

@@

\subsection{Relative error in neglecting the self-demagnetization}
